---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IFNallometry

<!-- badges: start -->
  [![R-CMD-check](https://github.com/emf-creaf/IFNallometry/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/emf-creaf/IFNallometry/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

The goal of IFNallometry is to provide routines for calculating volume and biomass for forest stands using allometries developed from Spanish Forest Inventory (IFN) plot data.

## Installation

You can install the development version of IFNallometry from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("emf-creaf/IFNallometry")
```

## Example

Here is an example data set of forest plot input to the package:

```{r example}
library(IFNallometry)
data("exampleTreeData")
head(exampleTreeData)
```

And here is the result of calculating timber volumes, using plot ID to extract the Spanish province:

```{r}
example_volumes <- IFNvolume(exampleTreeData, provinceFromID = TRUE)
head(example_volumes)
```

## Documentation

So far, the only documentation provided is the one included for package functions.

## Companion R packages

The development of **IFNallometries** is intended to complement packages [**medfate**](https://emf-creaf.github.io/medfate) and [**medfateland**](https://emf-creaf.github.io/medfateland) but it can be used independently. 



## Authorship

This R package is developed and maintained by the [*Ecosystem Modelling Facility*](https://emf.creaf.cat) unit at [*CREAF*](https://www.creaf.cat/) (in Spain), in close collaboration with researchers from  [*CTFC*](https://www.ctfc.cat/) (in Spain).

